---
title: "Individual Assignment 1"
author: "Paul Hoffman (450128)"
date: "9/20/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#a) Load Data, rows and colummns
```{r}
library(MASS)
Boston
?Boston
nrow(Boston) #rows in data set
ncol(Boston) #columns in data set
```

#b) Pairwise scatterplots
```{r}
pairs(Boston)
par(mfrow = c(2,2))
plot(Boston$age, Boston$crim) #As age increases there is a postive correlation to crime rate
plot(Boston$dis, Boston$crim) #As distance from employment center increases crime rates decrease
plot(Boston$tax, Boston$crim) #Tax does not seem to be that effected until greater than 650 and crime rate then increases
plot(Boston$nox, Boston$crim) #As nitrogen oxide concentration increases crime rates increase
```

#c) Predictors associated with per capita crime rate
```{r}
hist(Boston$crim, breaks = 100) #20% fall under crime rates
pairs(Boston[Boston$crim < 20, ]) #possible predictors include: zn, nox, age, dis, and ptratio
```

#d) Suburbs with high crime rates, tax rates, pupil-teacher ratios
```{r}
par(mfrow = c(3,1))
hist(Boston$crim) #about 20 suburbs with high crime rates
hist(Boston$tax) #crime rates have a influxes by tax from 200-400 and spike again around 650-700 (both in $10,000s)
hist(Boston$ptratio) #crime rates increase significantly at 20
```

#e) Suburbs bound by Charles River
```{r}
nrow(Boston[Boston$chas == 1, ]) #35 suburbs found bound by Charles River
```

#f) Median pupil-teacher ratio
```{r}
median(Boston$ptratio) #Median pupil-teacher ratio of 19.05 in the data set
```

#g) Lowest Median Value of owner-occupied homes, and other predictors
```{r}
min(Boston$medv) #$5000 is the lowest median value of owner-occupied homes
which.min(Boston$medv) #This is suburb 399 has the lowest median value
```
Possible predictors for this could include: age, dis, ptratio, and black

#h)Rooms
```{r}
summary(Boston$rm > 7) #total of avg rooms greater than 7 = 64
summary(Boston$rm > 8) #total of avg rooms greater than 8 = 13
plot(Boston$crim, Boston$rm)
plot(Boston$lstat, Boston$rm)
plot(Boston$medv, Boston$rm)
```
Rooms with greater than 8 rooms are not in line with crime rates, but seem to be in the lower 10% of lstat and average $50,000 in median value of owner-occupied homes so these homes are most likely to be owned by more affluent people
