---
title: "Individual Assignment 5"
author: "Paul Hoffman (450128)"
date: "10/18/2020"
output: html_document
---

#Exercise 6.8: Problem 8 (parts a, b, c, & d)

#Problem 8: In this exercise, we will generate simulated data, and will then use this data to perform best subset selection.

##(a) Use the rnorm() function to generate a predictor ğ‘‹ of length ğ‘›=100, as well as a noise vector of length ğ‘›=100

```{r}
set.seed(1)
n = 100
x = rnorm(100)
eps = rnorm(100)
```

#(b) Generate a response vector ğ‘Œ of length ğ‘›=100 according to the model ğ‘Œ=ğ›½0+ğ›½1ğ‘‹+ğ›½2ğ‘‹2+ğ›½3ğ‘‹3+ğœ– Where ğ›½0, ğ›½1, ğ›½2, and ğ›½3 are constants of your choice.

```{r}
y = 5 + 2*x + -1*x^2 + .6*x^3 + eps
```

#(c) Use the ğ‘Ÿğ‘’ğ‘”ğ‘ ğ‘¢ğ‘ğ‘ ğ‘’ğ‘¡ğ‘ () function to perform best subset selection in order to choose the best model containing the predictors ğ‘‹,ğ‘‹2,...,ğ‘‹10. What is the best model obtained according to ğ¶ğ‘, BIC, and adjusted ğ‘…2? Show some plots to provide evidence for your answer, and report the coefficients of the best model obtained. Note you will need to use the ğ‘‘ğ‘ğ‘¡ğ‘.ğ‘“ğ‘Ÿğ‘ğ‘šğ‘’() function to create a single data set containing both ğ‘‹ and ğ‘Œ.

```{r}
library(leaps)
data.full = data.frame(y = y, x = x)
regfit.full = regsubsets(y ~ poly(x, 10, raw = TRUE), data = data.full, nvmax = 10)
regfit.sum = summary(regfit.full)
```

```{r}
which.min(regfit.sum$cp)
```

```{r}
which.min(regfit.sum$bic)
```

```{r}
which.max(regfit.sum$adjr2)
```

```{r}
par(mfrow = c(2, 2))
plot(regfit.sum$cp, xlab = "Num of Variables", ylab = "Cp", type = "l")
points(3, regfit.sum$cp[3], pch=20, col="red", lwd=7)
plot(regfit.sum$bic, xlab = "Num ofVariables", ylab = "BIC", type = "l")
points(3, regfit.sum$bic[3], pch=20, col="red", lwd=7)
plot(regfit.sum$adjr2, xlab = "Num of Variables", ylab = "Adj R^2", type = "l")
points(3, regfit.sum$adjr2[3], pch=20, col="red", lwd=7)
```

```{r}
coef(regfit.full, which.max(regfit.sum$adjr2))
```


Here we find that all Cp, BIC, and Adj R squared all are chosen with three variables with models X, X^2, and X^5. 

#(d) Repeat (c), using forward stepwise selection and also using backwards stepwise selection. How does your answer compare to the results in (c)?

```{r}
#backward
regfit.back = regsubsets(y ~ poly(x, 10, raw = TRUE), data = data.full, nvmax = 10, method ="backward")

#forward
regfit.for = regsubsets(y ~ poly(x, 10, raw = TRUE), data = data.full, nvmax = 10, method ="forward")

backward.sum = summary(regfit.back)
forward.sum = summary(regfit.for)

which.min(backward.sum$cp)
```

```{r}
which.min(forward.sum$cp)
```

```{r}
which.min(backward.sum$bic)
```

```{r}
which.min(forward.sum$bic)
```

```{r}
which.max(backward.sum$adjr2)
```

```{r}
which.max(forward.sum$adjr2)
```

```{r}
par(mfrow = c(3,2))
plot(backward.sum$cp, xlab = "Num of Variables", ylab = "Backward Cp", type = "l")
points(3, regfit.sum$cp[3], pch=20, col="red", lwd=7)
plot(backward.sum$bic, xlab = "Num ofVariables", ylab = "Backward BIC", type = "l")
points(3, regfit.sum$bic[3], pch=20, col="red", lwd=7)
plot(backward.sum$adjr2, xlab = "Num of Variables", ylab = "Backward Adj R^2", type = "l")
points(3, regfit.sum$adjr2[3], pch=20, col="red", lwd=7)
plot(forward.sum$cp, xlab = "Num of Variables", ylab = "Forward Cp", type = "l")
points(3, regfit.sum$cp[3], pch=20, col="red", lwd=7)
plot(forward.sum$bic, xlab = "Num ofVariables", ylab = "Forward BIC", type = "l")
points(3, regfit.sum$bic[3], pch=20, col="red", lwd=7)
plot(forward.sum$adjr2, xlab = "Num of Variables", ylab = "Forward Adj R^2", type = "l")
points(3, regfit.sum$adjr2[3], pch=20, col="red", lwd=7)
```

```{r}
coef(regfit.for, which.max(forward.sum$adjr2))
```

```{r}
coef(regfit.back, which.max(backward.sum$adjr2))
```


Compared to part (c) we have the same criteria selected for the best subset. This is with each, whether forward or backward, 3 Numbers of Variables is be suited these are modeled with X, X^2, and X^5. 