---
title: "Individual Assignment 7"
author: "Paul Hoffman (450128)"
date: "11/7/2020"
output:
  word_document: default
  html_document: default
---

#Exercise 8.4: Problem 8 (parts a, b, & c)

##Problem #8: In the lab, a classification tree was applied to the Carseats data set after converting Sales into a qualitative response variable. Now we will seek to predict Sales using regression trees and related approaches, treating the response as a quantitative variable.

##(a) Split the data set into a training set and a test set.

```{r}
library(ISLR)
set.seed(1)
train = sample(1:nrow(Carseats), nrow(Carseats)/2)
carseats.train = Carseats[train, ]
carseats.test = Carseats[-train, ]
```

##(b) Fit a regression tree to the training set. Plot the tree, and interpret the results. What test MSE do you obtain?

```{r}
library(tree)
tree.carseats = tree(Sales ~ ., data = carseats.train)
tree.pred = predict(tree.carseats, carseats.test)
mean((tree.pred - carseats.test$Sales)^2)
plot(tree.carseats)
text(tree.carseats)
```

The test MSE is 4.148897

##(c) Use cross-validation in order to determine the optimal level of tree complexity. Does pruning the tree improve the test MSE?

```{r}
set.seed(1)
cv.carseats = cv.tree(tree.carseats)
plot(cv.carseats$size, cv.carseats$dev, type = "b")
which.min(cv.carseats$dev)
```

Here we see that the best tree would be with 8 nodes, so now we prune with 8 leafs.

```{r}
prune.carseats <- prune.tree(tree.carseats, best = 8)
plot(prune.carseats)
text(prune.carseats, pretty = 0)
```

```{r}
prune.pred = predict(prune.carseats, newdata = carseats.test)
mean((prune.pred - carseats.test$Sales)^2)
```

The test MSE increases from 4.148897 to 5.09085 due to pruning.